graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-04-30 paper/paper.Rmd
build with subcaptions
build paper without subcaption or subfig package

---
title: 'graphsim: An R package for simulating gene expression data from graph structures of biological pathways'
output:
  rmarkdown::pdf_document:
    fig_crop: no
    keep_md: TRUE
    fig_caption: yes
tags:
  - R
  - gene-expression
  - simulation
  - genomics
  - pathway
  - network
authors:
  - name: S. Thomas Kelly
    email: "tom.kelly@postgrad.otago.ac.nz, tom.kelly@riken.jp"
    orcid: 0000-0003-3904-6690
    affiliation: "1, 2" # (Multiple affiliations must be quoted)
  - name: Michael A. Black
    email: mik.black@otago.ac.nz
    orcid: 0000-0003-1174-6054
    affiliation: "1"
affiliations:
 - name: "Department of Biochemistry, University of Otago, PO Box 56, Dunedin 9054, New Zealand"
   index: 1
 - name: "RIKEN Center for Integrative Medical Sciences, Suehiro-cho-1-7-22, Tsurumi Ward, Yokohama, Kanagawa 230-0045, Japan"
   index: 2
date: 30 April 2020
bibliography: paper.bib
header-includes:
- \usepackage{caption}
- \usepackage{subfig}
---

@@

```{r, fig.align='center', fig.show='hold', fig.width='1.0\\linewidth', fig.height='1.0\\linewidth', out.height='.455\\linewidth', out.width='.455\\linewidth', fig.retina=20, fig.margin = FALSE, fig.cap = '\\textbf{Simulated graph structures.}. A constructed graph structure used as an example to demonstrate the simulation procedure inFigures 2 and 3. Activating links are denoted by black arrows and inhibiting links by red edges. Inhibiting edges have been highlighted in red.', fig.subcap=c("Activating pathway structure", "Inhibiting pathway structure")}
#generate graph structure

@@

plot_directed(graph, state ="activating", layout = layout.kamada.kawai,
              cex.node=3, cex.arrow=5, arrow_clip = 0.2)

@@

plot_directed(graph, state=state, layout = layout.kamada.kawai,
              cex.node=3, cex.arrow=5, arrow_clip = 0.2)
```

>>>>

---
title: 'graphsim: An R package for simulating gene expression data from graph structures of biological pathways'
output:
  rmarkdown::pdf_document:
    fig_crop: no
    keep_md: TRUE
    fig_caption: yes
tags:
  - R
  - gene-expression
  - simulation
  - genomics
  - pathway
  - network
authors:
  - name: S. Thomas Kelly
    email: "tom.kelly@postgrad.otago.ac.nz, tom.kelly@riken.jp"
    orcid: 0000-0003-3904-6690
    affiliation: "1, 2" # (Multiple affiliations must be quoted)
  - name: Michael A. Black
    email: mik.black@otago.ac.nz
    orcid: 0000-0003-1174-6054
    affiliation: "1"
affiliations:
 - name: "Department of Biochemistry, University of Otago, PO Box 56, Dunedin 9054, New Zealand"
   index: 1
 - name: "RIKEN Center for Integrative Medical Sciences, Suehiro-cho-1-7-22, Tsurumi Ward, Yokohama, Kanagawa 230-0045, Japan"
   index: 2
date: 30 April 2020
bibliography: paper.bib
header-includes:
  - \usepackage{caption}
 # - \usepackage{subfig}
---

@@

```{r, fig.align='center', fig.show='hold', fig.width='1.0\\linewidth', fig.height='1.0\\linewidth', out.height='.455\\linewidth', out.width='.455\\linewidth', fig.retina=10, fig.margin = FALSE, fig.cap = '\\textbf{Simulated graph structures.}. A constructed graph structure used as an example to demonstrate the simulation procedure inFigures 2 and 3. Activating links are denoted by black arrows and inhibiting links by red edges. Inhibiting edges have been highlighted in red.'}
#, fig.subcap=c("Activating pathway structure", "Inhibiting pathway structure")}
#generate graph structure

@@

plot_directed(graph, state ="activating", layout = layout.kamada.kawai,
              cex.node = 2, cex.arrow = 4, arrow_clip = 0.2,
              sub = "(a) Activating pathway structure", cex.sub = 1.5)

@@

plot_directed(graph, state=state, layout = layout.kamada.kawai,
              cex.node = 2, cex.arrow = 4, arrow_clip = 0.2,
              sub = "(b) Inhibiting pathway structure", cex.sub = 1.5)
```
